---
title: "Autoinjectors and Sustainability"
subtitle: "Sustainability analitics"
author: "Goran Nikolov, Marusa Storman, Incheol Jeong"
date: "2024-16-02"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "light"
    downcute_theme: "default"
    code_folding: hide
---

```{r setup, results = FALSE, message = FALSE }
## Options of this document

#global chunks options
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_chunk$set(message = TRUE)

#option for chunk caching.
cache = FALSE

#option for figure caching.
fig.cache = FALSE

```

# Introduction to plastic in medical devices and healthcare

Since 1970, the utilization of plastic in the healthcare sector has been steadily increasing. We have improved medical procedures and enhanced fluid management through the modernization of healthcare practices. Single-use plastic goods such as gloves and tubes enhance safety by reducing the danger of cross-contamination and illnesses, but they may also contribute to carbon emissions and climate change. Single-use plastic, while effective for our protection, poses an increasing waste management problem. Improper disposal and use of such items greatly increase CO2 emissions. There is no precise data on the quantity of plastic trash in medicine, although certain research indicates that plastic could make up to 30% of the total waste in healthcare.



# Overview of Autoinjectors as Medical Devices 

autoinjectorss have become a cornerstone in the administration of life-saving medications, offering patients a convenient, reliable, and safe method to administer drugs with precision and ease. These devices, designed for single-use or limited-use scenarios, have significantly improved the quality of life for individuals with chronic conditions such as diabetes, rheumatoid arthritis, and severe allergies. Their ease of use not only enhances patient compliance but also minimizes the potential for dosing errors, making them an invaluable tool in modern healthcare.

## The Importance of Sustainability in Medical Devices

The concept of sustainability within the medical device industry has garnered increasing attention, driven by a growing awareness of environmental issues and the healthcare sector's substantial environmental footprint. Sustainability in medical devices encompasses the entire lifecycle of a product, from design and manufacturing to use and disposal. It involves assessing and minimizing environmental impacts, such as waste generation, energy consumption, and carbon emissions, while also considering social and economic factors.

## The Challenge of Sustainability in Autoinjectors

Despite their benefits, the sustainability of autoinjectors presents a unique challenge. The majority are designed for single use to ensure sterility and safety, leading to a significant amount of medical waste. This is compounded by the complex mix of materials used in their construction, including plastics, metals, and electronic components in some cases, which complicates recycling efforts. The increasing reliance on autoinjectors for a variety of medications necessitates a critical examination of their environmental impact and the exploration of sustainable alternatives.

## Objevtives of this study

This study aims to explore the sustainability of autoinjectors, focusing on their environmental, social, and economic impacts. It seeks to understand the current landscape of autoinjector usage, identify the key challenges to their sustainability, and evaluate potential strategies for improving their environmental footprint. By doing so, the study contributes to the broader discourse on sustainable healthcare practices and the role of medical devices in achieving a more sustainable future.



# Casual loop map for production cycle of the autoinjectors

We intended to illustrate via graphics how utilizing Loopy to reuse plastic can lead to the creation of a sustainable environment. Initially, producing plastic for medical autoinjectors impacts four areas during this procedure.

One factor is the carbon emissions generated during the manufacturing of autoinjectors. The second factor is the carbon emissions generated by transporting manufactured autoinjectors to the market. Thirdly, discarded autoinjectors contribute significantly to plastic pollution. The creation of these plastic objects serves as a reminder to prioritize recycling.

Excluding the plastic recycling flowchart from this process would result in significant carbon emissions. The recycling graphic will help reduce carbon emissions and plastic waste. Reusing plastic from autoinjectors will decrease the need for producing new products, therefore lowering carbon emissions associated with product transportation. Therefore, the recycling diagram visually demonstrates how the process decreases overall carbon emissions by incorporating arrows that signify a reduction in carbon emissions in contrast to arrows indicating an increase in carbon emissions.

The inclusion of the 'recycling' figure leads to a reduction in carbon emissions across the entire process. The 'recycling' diagram is crucial for sustainable development. We believe that the reuse of autoinjectors we are concentrating on will make important contributions to addressing the climate change affecting humanity.


```{r, echo=FALSE, results='asis'}
cat('
<div style="overflow: hidden; width: 100%; height: 800px; transform: scale(1.1); transform-origin: top left;">
  <iframe src="https://ncase.me/loopy/v1.1/?embed=1&data=[[[1,408,47,1,%22CO2%2520Emission%22,4],[2,55,268,1,%22Plastic%22,5],[3,244,514,1,%22Transportation%22,0],[4,537,533,1,%22Waste%22,1],[5,726,254,1,%22Recycle%22,3]],[[2,1,94,1,0],[3,1,-50,1,0],[1,5,72,1,0],[5,1,49,-1,0],[5,4,-57,-1,0],[4,5,21,1,0],[2,5,28,1,0],[5,2,39,1,0],[2,4,171,1,0],[2,3,-4,1,0],[4,1,-48,1,0]],[[405,-42,%22Final%2520goal%2520to%2520reduce%22],[49,194,%22First%2520start%2520point%22],[72,53,%22Making%2520CO2%2520in%2520the%2520process%2520of%2520making%2520plastic%22],[-18,425,%22Need%2520to%2520be%2520carried%2520from%2520factory%2520to%2520retailer%22],[892,267,%22The%2520most%2520important%2520part%22]],6%5D" width="700" height="500" style="border: none; overflow: hidden;"></iframe>
</div>
')
```

# The 17 sustainable development goals

Single-use medical devices intersect with several Sustainable Development Goals (SDG) due to their impact on health, environment, and innovation:

- **SDG 3 (Good Health and Well-being):** These devices are crucial in delivering healthcare, including vaccinations and self-administered medications for chronic diseases, directly contributing to improving health outcomes.
- **SDG 9 (Industry, Innovation, and Infrastructure):** The development of single-use medical devices involves innovation in healthcare technologies, promoting the industry's growth and infrastructure.
- **SDG 12 (Responsible Consumption and Production):** The production, use, and disposal of single-use medical devices raise significant concerns about waste and sustainability, urging a shift towards more responsible consumption patterns and efforts to reduce environmental impact.
- **SDG 13 (Climate Action):** The lifecycle of single-use medical devices, from production to disposal, can contribute significantly to carbon emissions, making the reduction of this impact aligned with climate action efforts.

These connections highlight the importance of integrating health, innovation, and environmental sustainability considerations in the development and use of single-use medical devices.

```{r SDG, echo=FALSE, results='asis'}
cat('<div style="display: grid; grid-template-columns: repeat(6, 1fr); gap: 20px;">')
for (i in 1:17) {
  logo_path <- paste0("C:/Users/Nikolov/Downloads/E-Inverted-Icons-WEB/E Inverted Icons WEB/E Inverted Icons_WEB-", sprintf("%02d", i), ".png")
  cat(sprintf('<img src="%s" style="width: 100%%; max-width: 200px;">', logo_path))
  if (i == 17) { # For visual balance, as there's no 18th logo
    cat('<div></div><div></div>') # Fill the remaining grid cells
  }
}
cat('</div>')
```

## Impact and stakeholders table based on the SDG goals

```{r sdg table, message=FALSE, warning=FALSE}
# Load required libraries
library(knitr)
library(kableExtra)

# Create dataframe for the table
SDGTable <- data.frame(
  Aspect = c("SDG 3 (Good Health and Well-being)", "SDG 9 (Industry, Innovation, and Infrastructure)", 
             "SDG 12 (Responsible Consumption and Production)", "SDG 13 (Climate Action)"),
  Social_Impact = c("Improves access to healthcare and outcomes, particularly in vaccinations and chronic disease management.",
                    "Enhances healthcare quality and access through technological advancements.",
                    "Raises awareness about environmental sustainability and encourages responsible consumption.",
                    "Promotes public and organizational commitment to reducing carbon footprint."),
  Economic_Impact = c("Drives demand for healthcare products, potentially increasing healthcare costs.",
                      "Promotes economic growth through the development of new technologies and infrastructure.",
                      "May increase costs for sustainable production and disposal methods.",
                      "Encourages investment in green technologies and practices, potentially leading to economic opportunities."),
  Industrial_Impact = c("Stimulates innovation in medical technologies and healthcare services.",
                        "Encourages the development of innovative healthcare solutions and infrastructure.",
                        "Challenges the industry to develop sustainable materials and waste management solutions.",
                        "Puts pressure on the industry to innovate in eco-friendly production, packaging, and disposal methods."),
  Stakeholders_Impacted = c("Patients, healthcare providers, healthcare industry.",
                            "Innovators, healthcare industry, government.",
                            "Consumers, healthcare providers, environmental organizations, industry regulators.",
                            "Environmental organizations, governments, industry, global community.")
)

# Print formatted table with colors
kable(SDGTable, caption = "Sustainability Aspects and Impacts", format = "html", align = "c") %>%
  kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE, color = "white", background = "lightblue") %>%
  row_spec(1:4, background = "#f2f2f2")

```

# General overview

There is no available data on these medical devices, auto-injectors. However, we have valuable information from the industry that we used to produce synthetic data to analyze the demand and market for auto-injectors.

## Data view

We can conduct a little exploration of our data from these 6 rows to understand the meaning of the variables.


```{r loading the data, message=FALSE, warning=FALSE}
library(readr)
data <- read_csv("data_autoinjectors_clean.csv")

# Round numeric columns to two decimals
numeric_cols <- sapply(data, is.numeric)
data[numeric_cols] <- round(data[numeric_cols], digits = 2)

library(DT)
datatable(
  data,
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; color: black; font-size: 20px; font-weight: bold; text-align: center;',
    'Dataframe autoinjectors'
  )
)
```

- The **year** indicates the specific year when the data was collected. The data is stored as a numeric (dbl) data type.
- **Demand**, measured in millions, indicates the need for a specific type of autoinjector, stored as a dbl.
- **Injector Type** indicates the specific type of injector that was utilized. It is stored as a character data type.
- The **Material Type** indicates the specific material utilized. It is stored as a character data type.
- **Volume Produced** refers to the quantity of autoinjectors manufactured. The data is stored as a dbl.
- **Reusable** shows if the goods or service may be used again. The data is kept as a numeric (dbl) type, with 0 indicating non-reusable and 1 indicating reusable.
- The term **"recyclable"** specifies whether the autoinjector may be recycled. The data is kept as a logical (lgl) type, with TRUE indicating recyclable and FALSE indicating non-recyclable.
- **Usage Frequency** is a measure of how often something is used. It is stored as a character data type.
- **Efficacy rate** indicates the effectiveness of the autoinjector. The data is saved as a numeric data type(dbl).
- **Carbon Footprint** indicates the carbon footprint linked to each observation. The data is saved in a numeric data type (dbl). The values in this column indicate the estimated carbon footprint in a specific unit (e.g., kilos of CO2 equivalent) for each observation.


# EDA - Exploration Data Analysis

In order to arrive at conclusions that are plausible on the basis of the synthetic data that we have generated, we will make use of a number of different data exploration methods and functions.

## Boxplot Data Exploration

Our ability to study different kinds of plastics and determine their respective carbon footprints is made possible by the utilization of a Boxplot diagram. Plastics are able to be categorized according to the number of times they are used in auto injectors. Across all usage frequencies, the carbon footprint figures for the recyclable plastic are the lowest for all combinations. It is recommended that users first click on the material type, and then proceed to navigate through the interface's various boxplots in order to investigate the user-friendly features.


```{r data exploration, message=FALSE, warning=FALSE}
library(plotly)

intusage <- ggplot(data, aes(x = `Usage Frequency`, y = `Carbon Footprint`, fill = `Material Type`)) +
  geom_boxplot() +
  labs(title = "Boxplot of Carbon Footprint by Usage Frequency and Material Type",
       x = "Usage Frequency",
       y = "Carbon Footprint",
       fill = "Material Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggplotly(intusage)

```


```{r summurising the data, message=FALSE, warning=FALSE}
summary(data)
```

In view of the summary that has been provided, we are able to draw a number of conclusions concerning the dataset that pertains to auto injectors:

- **Demand Trends:** The demand for autoinjectors has varied over the years, with a minimum demand of 50 million units and a maximum of 1836.19 million units. The median demand is approximately 96.84 million units, indicating that demand tends to be moderate.
- **Injector Types and Materials:** The data set includes information about different types of injectors and the materials used. This suggests variability in product design and construction, which may have implications for performance and sustainability.
- **Volume Produced:** The volume produced varies widely, with a range from 13,145 units to over 2.2 million units. This suggests differences in manufacturing capabilities and market demand across different time periods.
- **Sustainability Features:** A subset of the injectors is marked as reusable or recyclable, with approximately 19.3% of the injectors being reusable. This indicates a consideration for sustainability in product design, although there is room for improvement.
- **Usage Frequency:** The majority of injectors have a usage frequency of 1, indicating that they are intended for single use.
- **Carbon Footprint:** The carbon footprint associated with producing the injectors varies widely, with a minimum value of 8036 and a maximum of 3,660,018. This indicates potential differences in manufacturing processes and materials used, which depends also on the demand for autoinjectors.
- **Recyclable Type and Material Category:** Information about recyclability and material categories provides insight into the sustainability profile of the injectors. This data can be further analyzed to understand the environmental impact of different product designs and materials.

## Linear Model Comparation

By comparing a basic linear model between non-recyclable and recyclable auto injectors, conclusions can be drawn.


```{r linear model comp, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)

#Merge plastic 1 and 2 as non-recyclable
data <- data %>%
  mutate(MaterialCategory = case_when(
    `Material Type` %in% c("Type1 Plastic", "Type2 Plastic") ~ "Non-Recyclable",
    TRUE ~ "Recyclable"
  ))

 #Plot to compare CO2 between recyclable and non-recyclable materials
lindata <- ggplot(data, aes(x = Year, y = `Carbon Footprint`, color = `MaterialCategory`)) +
  geom_smooth(method = "lm", se = FALSE) + 
  scale_color_manual(values = c("Recyclable" = "skyblue", "Non-Recyclable" = "red")) +
  theme_minimal() +
  labs(title = "Carbon Footprint Trends by Material Category",
       x = "Year",
       y = "Carbon Footprint",
       color = "Material Category") +
  theme(legend.position = "bottom")

# Convert ggplot object to an interactive Plotly plot
ggplotly(lindata)
```


Through the linear function diagram, it is evident that the carbon footprint has been increasing since 2010 and is projected to continue growing significantly in the coming years. A comparison between non-recyclable and recyclable injectors reveals that recycling auto injectors could reduce the carbon footprint by approximately 50%. This reduction could have a substantial impact on global climate change and sustainable manufacturing in the health industry.

## Density Plot

The density map will illustrate the density of recyclable and non-recyclable materials, categorized by the count of auto injector types, summarized according to carbon emissions. 

```{r density plot, message=FALSE, warning=FALSE}
#density plot 
densplot <- ggplot(data, aes(x = `Carbon Footprint`, fill = Recyclable)) +
  geom_histogram(data = subset(data, Recyclable == TRUE), binwidth = 100000, alpha = 0.6, color = "black") +
  geom_histogram(data = subset(data, Recyclable == FALSE), binwidth = 100000, alpha = 0.6, color = "black") +
  scale_fill_manual(values = c("TRUE" = "skyblue", "FALSE" = "red")) + # Light blue for recyclable, light pink for non-recyclable
  theme_minimal() +
  labs(title = "Carbon Footprint: Recyclable vs. Non-Recyclable Materials", x = "Carbon Footprint", y = "Count")
ggplotly(densplot)
```

The diagram makes it clear that the majority of the recyclable autoinjectors are situated on the left side, which indicates that they have a smaller carbon footprint. It is intriguing to note, however, that recyclable autoinjectors are not significantly connected with decreased levels of carbon emissions being produced. The fact that this is the case shows that there is not enough production of recyclable autoinjectors to compensate for the carbon emissions that are caused by non-recyclable autoinjectors, which are dispersed through the whole diagram.

## Forecasting with Linear Function

In the absence of recycling or the utilization of biodegradable materials, the following line plot will present the anticipated carbon footprint starting in the year 2030 and continuing through the year 2040.

```{r forecast, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(forecast)


# Aggregate data by Year
data_aggregated <- data %>%
  group_by(Year) %>%
  summarise(`Total Carbon Footprint` = sum(`Carbon Footprint`, na.rm = TRUE))

# Fit a linear model
model <- lm(`Total Carbon Footprint` ~ Year, data = data_aggregated)

# Generate forecasts for years after 2030
future_years <- data.frame(Year = (2031:2040)) # Adjust the range as needed
predictions <- predict(model, newdata = future_years)

# Combine historical and forecasted data
future_years$`Total Carbon Footprint` <- predictions
combined_data <- rbind(data_aggregated, future_years)

# Visualize with ggplot2 and make interactive with plotly
plot <- ggplot(combined_data, aes(x = Year, y = `Total Carbon Footprint`)) +
  geom_line() +
  geom_point(color = "red") +
  theme_minimal() +
  labs(title = "Carbon Footprint Forecast Beyond 2030",
       x = "Year",
       y = "Total Carbon Footprint")
ggplotly(plot)

```

According to the plot, it is evident that the prediction beyond 2030 will be critical for adding 10 million tons of CO2 into the atmosphere alone from the production of auto injectors in the healthcare industry. This can have a significant impact on society both locally and globally.

## Efficacy Rate Analysis

After conducting the efficacy rate analysis, it has become abundantly clear that auto injectors that haven't been used but have been made are likewise a significant contributor to carbon emissions in the overall scenario. Both recycling plastic and making use of artificial learning. are potential ways to cut down on waste. Predicting the demand for autoinjectors in the market is possible with the use of machine learning. In addition, a sustainable approach could consist of replacing only the injection cartridges of autoinjectors that contain medicine that has expired but are still operational mechanically. According to Sustainable Development Goal 9, this strategy can be implemented as smart manufacturing.


```{r savings, message=FALSE, warning=FALSE}
#Efficacy rate exploration

#1 potential co2 savings 
# Total CO2 emissions by year and efficacy rate
co2_summary <- data %>%
  group_by(Year, `Efficacy rate`) %>%
  summarise(TotalCarbonFootprint = sum(`Carbon Footprint`, na.rm = TRUE)) %>%
  ungroup()


# Potential savings
total_co2_by_year <- co2_summary %>%
  group_by(Year) %>%
  summarise(TotalCarbon = sum(TotalCarbonFootprint, na.rm = TRUE))

co2_savings <- merge(co2_summary[co2_summary$`Efficacy rate` == 1, ], total_co2_by_year, by = "Year")
co2_savings$PotentialSavings = co2_savings$TotalCarbon - co2_savings$TotalCarbonFootprint

# Plotting
savef <- ggplot() +
  geom_bar(data = co2_summary, aes(x = Year, y = TotalCarbonFootprint, fill = as.factor(`Efficacy rate`)), stat = "identity", position = "dodge") +
  geom_line(data = co2_savings, aes(x = Year, y = TotalCarbon, group = 1), color = "black", linetype = "dashed") +
  geom_point(data = co2_savings, aes(x = Year, y = TotalCarbon), color = "red", size = 3) +
  scale_fill_manual(values = c("0" = "red", "1" = "skyblue")) +
  theme_minimal() +
  labs(title = "Annual CO2 Emissions and Potential Savings with 100% Efficacy",
       x = "Year",
       y = "Total Carbon Footprint (CO2 Emissions)",
       fill = "Efficacy Rate") +
  guides(fill = guide_legend(title = "Efficacy Rate"))
ggplotly(savef)
```

# Forecasting with ARIMA

ARIMA can be utilized to anticipate future carbon emissions and determine the potential reduction in carbon footprint by implementing 5% recycling and 3% biodegradable plastic annually.

## ARIMA Model Evaluation Based on Historical Data

```{r forecasting with arima, message=FALSE, warning=FALSE}
library(forecast)

# Use auto.arima to find an optimal ARIMA model automatically
optimal_arima_model <- auto.arima(data_aggregated$`Total Carbon Footprint`)

# Forecast beyond 2030
arima_forecast <- forecast(optimal_arima_model, h = 10) # next 10 years

# Visualize the forecast (non-interactive)
autoplot(arima_forecast) + 
  labs(title = "ARIMA Forecast of Carbon Footprint Beyond 2030",
       x = "Year", y = "Total Carbon Footprint")

summary(arima_forecast)
```


The provided ARIMA forecast summary offers valuable insights into the future trends of the Total Carbon Footprint based on the historical data aggregated yearly. The selected ARIMA(0,1,0) model, also known as a Random Walk model, suggests that the best fit for forecasting the series under consideration does not rely on auto-regressive (AR) or moving average (MA) components but on differencing the series once (I(1)) to achieve stationarity.


- **Model Type**: ARIMA(0,1,0) indicates a model that uses differencing to render the time series stationary but does not utilize AR or MA components. This simplicity often suits series where future values primarily mirror past values with minor variations.
- **Sigma^2**: The variance of the residuals (σ^2 = 2.819e+14) is quite large, indicating significant variability in the forecast errors. This suggests that while the model can capture the general trend of the data, there's considerable uncertainty in the predictions.
- **Log Likelihood and Information Criteria**: The log likelihood value is -361.11, with AIC, AICc, and BIC scores being 724.21, 724.43, and 725.21, respectively. Lower values of AIC and BIC indicate a better model fit, but without comparison models, these values mainly serve to guide model refinement. The closeness of AIC and AICc indicates that the correction for finite sample sizes does not significantly impact the model's evaluation.
- **Error Measures**: The error metrics (ME, RMSE, MAE, MPE, MAPE, MASE, ACF1) highlight the model's performance in the training set. Notably, the MAE (Mean Absolute Error) and RMSE (Root Mean Squared Error) are quite high, which, along with a substantial ME (Mean Error), points to the model's limited accuracy in capturing the data's variability. The MAPE (Mean Absolute Percentage Error) of approximately 31% further emphasizes the forecast's average percentage error per step.

## ARIMA model evaluation based on hypothetical values

We will attempt to minimize the carbon footprint by using annual reduction rates of 5% due to enhanced recycling and an additional 3% reduction with biodegradable plastics in the upcoming model.

```{r hypothetical anual reduction rate, message=FALSE, warning=FALSE}
# Hypothetical annual reduction rates
recycling_reduction_rate <- 0.05 # 5% reduction per year due to increased recycling
biodegradable_reduction_rate <- 0.03 # 3% additional reduction with biodegradable plastics

# Apply reductions to forecasted values
adjusted_forecast <- arima_forecast$mean * (1 - recycling_reduction_rate - biodegradable_reduction_rate) ^ seq(1, 10)

# Create a data frame for adjusted forecast
years <- seq(2031, 2040)
adjusted_forecast_df <- data.frame(Year = years, `Adjusted Carbon Footprint` = adjusted_forecast)

# Plotting the adjusted forecast
acf <- ggplot(adjusted_forecast_df, aes(x = Year, y = `Adjusted.Carbon.Footprint`)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  theme_minimal() +
  labs(title = "Adjusted Carbon Footprint Forecast with Recycling and Biodegradable Plastics",
       x = "Year", y = "Adjusted Carbon Footprint")
ggplotly(acf)
```

It is evident from the diagram that by utilizing only the provided percentage, we may decrease the carbon footprint impact by about 25 million tons in 5 years, a value that is not subject to depreciation. By implementing these approaches sooner, we will undoubtedly be more effective by 2030, aiming to reduce our carbon footprint and achieve even greater value by 2040.


# Conclusion

Plastic in healthcare, especially autoinjectors, raises concerns about environmental sustainability, public health, and innovation. This study emphasizes the need to balance medical plastic's benefits with its environmental impact. Disposable medical gadgets have increased medical waste and carbon emissions, which threatens sustainability despite their benefits for healthcare and patient safety.

Researching autoinjector sustainability shows that medical device innovation and flexibility are essential. Autoinjectors are convenient and effective, but they are single-use and made of complex materials, making recycling difficult and increasing the healthcare sector's environmental impact. This study stresses recycling, biodegradable materials, and sustainable production to reduce environmental effect.

Linking single-use medical equipment to other SDGs shows how medical waste management affects global health, innovation, and climate action. Data analysis and predictive models like ARIMA show the challenges and opportunities to reduce carbon emissions by recycling and using biodegradable materials.

As healthcare evolves, medical equipment life cycles must be sustainable. This demands rethinking materials, manufacturing methods, and end-of-life disposal. Manufacturers, healthcare professionals, policymakers, and patients must work together to encourage innovative methods that conserve the environment while maintaining high standards of care.